%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume-openfont} % Use US Letter paper, change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

%\namesection{Thomas}{Wells}
\namesection{Marly}{Puckett}
{
%\urlstyle{same}\url{https://github.com/mpuckett159} \\ % Your website, LinkedIn profile or other web address
%US citizen \\
%\href{mailto:thomas.wells@protonmail.ch}{thomas.wells@protonmail.ch} | 929.256.2382
\href{mailto:mpuckett259@gmail.com}{mpuckett259@gmail.com} | 206.889.3135 | Github:// \href{https://github.com/mpuckett159}{\bf mpuckett159 } \\

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
%----------------------------------------------------------------------------------------
%	INTRODUCTION SECTION
%----------------------------------------------------------------------------------------
\section{Introduction}
\begin{flushleft}
I am an expert in production infrastructure automation, with a specialty in modernization of on-prem systems. I am passionate about open source development and improving user experiences, be they developers, operations, or end users.
\end{flushleft}
\vspace{-10pt}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.28\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}
\subsection{University of Houston}

\descript{BS Mathematics}
\location{2014}

%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Open Source Work
%------------------------------------------------

\section{Open Source}
\subsection{Kubernetes}
SIG-CLI reviewer.  I work with a team to maintain the quality of kubectl, including triaging issues, review contributions, running the bi-weekly bugscrub, and ensure testing coverage. I am currently working on implementing KEP-3104, which is a .bashrc-like config file to enable more flexible configuration. I am also working on improvements to the jsonpath functionality. \\

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Most Proficient:}
 Python \textbullet{} Go \textbullet{} JavaScript \textbullet{} SQL \\[7pt]
\location{Infrastructure}
 AWS \textbullet{} Docker \textbullet{} Kubernetes \\
 DigitalOcean \textbullet{} Terraform \\
 Ansible \\[7pt]
\location {Frameworks:}
 Flask \textbullet{} Gorilla \\[7pt]
\location {Testing:}
 Inspec \textbullet{} Pytest \textbullet{} Go testing \\[7pt]

\sectionspace
\vspace{-10pt} % Tighten up the side columns a tad

%------------------------------------------------
% Certifications
%------------------------------------------------

\section{Certifications}
\subsection{\RaggedRight{Certified Kubernetes Administrator}}
 November 9th, 2021 \\
 
\sectionspace

\subsection{Terraform Associate}
October 1st, 2021

\sectionspace % Some whitespace after the section
\vspace{-10pt} % Tighten up the side columns a tad

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.70\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Lyell Immunopharma}\\
\descript{Senior Software Engineer}

\location{March 2022 - Present | Seattle, WA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Implemented an automated system for management of Amazon Workspaces to streamline deployments, reducing Workspace deployment times from months to minutes.
\item Improved stability of our CI/CD pipelines by setting development standards for dependency management and code health, enforcing continuous updates to repositories and nightly builds, and improving scripting with better error handling and messages. Additionally, invested in developer education and documentation, empowering them to deliver products and features faster.
\item Mentor other members of DevSecOps team in standardization and practices, especially around operationalization of our codebase, providing clear and up-to-date documentation to reduce ticket load for support with using our tooling, and a bias towards simplifying development pipelines and infrastructure architectures.
\item Expanded our testing framework and code coverage using go-task, inspec, and pytest, including implementing proper unit testing for our terraform code.
\end{tightitemize}

\sectionspace

\runsubsection{AHEAD \normalfont\small (Kovarus pre-acquisition)} \\
\descript{Senior Technical Consultant}

\location{April 2018 - March 2022 | Seattle, WA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Worked closely with clients to design and implement infrastructure automation systems to solve their business use cases.
\item Designed development environment by defining user stories, developing orchestration workflows, defining development best practices, building CI/CD pipelines and defining code promotion strategies using a variety of languages and tools.
\item Concluded each project with detailed documentation and knowledge transfer sessions.
\item Helped develop reusable assets and code for the delivery team to improve our delivery velocity and increase margins on sales deals.
\item Mentored other engineers on a variety of topics to maintain a strong cross functional knowledge base to provide clients with a broad and deep pool of technical expertise.
\item Balanced clients existing tools with improvements in newer technologies, providing recommendations for modernization where it provides the most benefit.

\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{Verizon Enterprise Solutions}\\
\descript{Assigned Client Engineer}

\location{July 2016 - April 2018 | Houston, TX}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Spearhead the modernization of a legacy environment to a private cloud to enable significant improvements for a \$3B/yr e-commerce website. This reduced environment deployment times from 4 months to 3.5 hours, dramatically increasing the velocity that developers could ship features at.
\item Maintained on going support of the environment, developing new features, improving existing features, and implementing bug fixes. This included the hardware, the hypervisors, the automation and orchestration engines, the workflows, the virtual machines, the operating systems, the software defined firewalls and routers, and the load balancers.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}